\documentclass[12pt]{article}
\usepackage{pgfplotstable}
\usepackage{array}

\title{Percentage of Water in Popcorn}
\author{Zach Latta, Angel Madrid, Bailey Frierson, Samantha Lee, Griffin Troy}

\begin{document}

\maketitle

\section{Data Table}

\pgfplotstabletypeset[
  col sep=comma,
  string type,
  every head row/.style={before row=\hline,after row=\hline},
  every last row/.style={after row=\hline},
] {masses.csv}
\\\\
Important note: masses include mass of beaker

\section{Questions}

\subsection{Lab Safety}

\begin{enumerate}
  \item What lab safety precautions should be taken when working with Bunsen Burners?
    \begin{itemize}
      \item Wear safety goggles. Avoid touching the upper area of the tube, it
        is hot. Verify that the gas is working properly.
    \end{itemize}
  \item Name the various pieces of laboratory that were used in the lab today.
    \begin{itemize}
      \item Bunsen Burner
      \item Tongs
      \item Gas
      \item Ringstand
      \item Iron ring
      \item Wire gauze
    \end{itemize}
\end{enumerate}

\subsection{Analysis}

\begin{enumerate}
  \item Determine the mass of 10 unpopped popcorn kernels for each brand of
    popcorn.
    \begin{itemize}
      \item Nice popcorn: $m = 2.6 = 97.4 - 94.8$, $26 = m * 10$. The mass of
        10 unpopped Nice popcorn kernels is $26$g.
      \item Orville popcorn: $m = 3.1 = 96.9 - 94.3$, $31 = m * 10$. The mass
        of 10 unpopped Orville popcorn kernels is $31$g.
    \end{itemize}
  \item Determine the mass of 10 popped popcorn kernels for each brand of popcorn.
    \begin{itemize}
      \item Nice popcorn: $m = 2.1 = 96.9 - 94.8$, $21 = m * 10$. The mass of
        10 popped Nice popcorn kernels is $21$g.
      \item Orville popcorn: $m = 2.2 = 96.5 - 94.3$, $22 = m * 10$. The mass
        of 10 popped Orville popcorn kernels is $22$g.
    \end{itemize}
  \item Determine the mass of water that was lost when the popcorn popped for each brand.
    \begin{itemize}
      \item Nice popcorn: $\ell = 0.5 = 97.4 - 96.9$. The volume of water lost
        while popping Nice kernels is $0.5$mL.
      \item Orville popcorn: $\ell = 0.4 = 96.9 - 96.5$. The volume of water
        lost while popping Orville kernels is $0.4$mL.
    \end{itemize}
\end{enumerate}

\subsection{Conclusions}

\begin{enumerate}
  \item Determine the percentage by pass of water in each brand of popcorn.
    \begin{itemize}
      \item Nice popcorn: $m = 2.6$, $\ell = 0.5$,
        $p = 0.192 = \frac{\ell}{m}$. Approximately $19.2$\% of Nice popcorn
        kernels is water.
      \item Orville popcorn: $m = 2.2$, $\ell = 0.4$,
        $p = 0.182 = \frac{\ell}{m}$. Approximately $18.2$\% of Orville popcorn
        kernels is water.
    \end{itemize}
  \item Do all brands of popcorn contain approximately the same percentage of water?
    \begin{itemize}
      \item Yes, all brands of popcorn contain approximately the same
        percentage of water.
    \end{itemize}
  \item What are some likely areas of error in this experiment?
    \begin{itemize}
      \item Likely areas of error include, but are not limited to, distribution
        of popcorn kernels in the beaker, time beaker is left on the Bunsen
        burner, and inconsistent coating of kernels with oil.
    \end{itemize}
\end{enumerate}

\end{document}
